Datasheet for 'Canadian Grocery Prices

### 2024-11-28 other/datasheet/datasheet.qmd
date fixed

---
title: "Datasheet for 'Canadian Grocery Prices'"
subtitle: "The Project Hammer Dataset"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: [https://jacobfilipp.com/hammer/](https://jacobfilipp.com/hammer/)."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for 'Canadian Grocery Prices'"
subtitle: "The Project Hammer Dataset"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: [https://jacobfilipp.com/hammer/](https://jacobfilipp.com/hammer/)."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---
